Selecting and Controlling Physical Devices Through Head-Mounted Infrared Targeting

### 2013-09-03 doc/sigchi14/introduction.tex
add thoughts in introduction > drawbacks of existing work

\bjoern{what are the drawbacks of this existing work?}
Some drawbacks of using handheld devices are that the device first has to be retrieved (e.g., from a pocket) and aimed; that two hands may be necessary for operation (one to hold the device, one to operate the touch screen); and that the user's visual attention is split between looking down at a screen and out at the device to-be-controlled. \bjoern{these all sound kind of weak.} These general limitations have led researchers to investigate ``always-available'' physiological input modalities for phones on one hand~\cite{morris_emerging_2011}, and wearable computing devices on the other hand.

>>>>

\bjoern{what are the drawbacks of this existing work?}
Some drawbacks of using handheld devices are that the device first has to be retrieved (e.g., from a pocket) and aimed; that two hands may be necessary for operation (one to hold the device, one to operate the touch screen); and that the user's visual attention is split between looking down at a screen and out at the device to-be-controlled. \bjoern{these all sound kind of weak.} \sean{When the number of smart devices increases, it also takes time to traverse within a list of dozens of items. In addition, mapping the name of a device to its real physical presence is not always intuitive. For example, it is hard to identify where is ``light in area E'' in an office building. Moreover, in a shared space, the person trying to control the device might not be the one that named it. } These general limitations have led researchers to investigate ``always-available'' physiological input modalities for phones on one hand~\cite{morris_emerging_2011}, and wearable computing devices on the other hand.
